Sound and Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants \thanks{Supported by EPSRC grant EP/J012564/1, ERC project 280053 (CPROVER) and the H2020 FET OPEN SC$^2$.}

### 2017-02-16 hscc2017/paper.tex
wording

Within the scheme in Figure \ref{fig:CEGIS}, 
while the {\sc synthesise} phase searches for potentially unsound 
candidate solutions, the soundness of the model is ensured by the {\sc verify} phase.  
If a candidate solution is successfully verified, it is necessarily sound.

Through its two stages, the {\sc verify} phase looks at two separate elements for
soundness.
% The first ensures that there exists no
% counterexample plant that would create a closed-loop with unstable
% poles. The fixed word length of the controller is not relevant at this
% point since the parameters have already been chosen to fit this
% criteria (i.e., the candidate solution is FWL).
The first stage ensures that no counterexample
plant with an unstable closed loop exists with % If no such
% system exists, then the controller is stable for all
% plants in the collection with
the limitations given by the data
type used by the verifier. Since the actual
plant works in the reals, whereas we use fixed/floating point
arithmetic to evaluate it, we need to ensure that the rounding errors
in the caculations do not cause the solution to be unsound.
% 
For this reason the second verification stage uses interval arithmetic with
outward rounding to ensure that these errors do not exceed critical
bounds that could make some plant unstable.

This means that whilst the solution may not be complete, it is sound for
evaluating any collection of real plants with a defined FWL controller. 
We require two verification stages because,
while the second one can ensure the stability of all plants in the collection, 
it is unable to provide a counterexample.

>>>>

The {\sc synthesise} phase generates potentially unsound candidate
solutions.  The soundness of the model is ensured by the {\sc verify} phase. 
If a candidate solution passes verification, it is necessarily sound.

The {\sc verify} phase considers two aspects of soundness.  The first stage
ensures that no counterexample plant with an unstable closed loop exists
over finite-precision arithmetic.  Since the actual plant uses reals, we
need to ensure we do not miss a counterexample because of rounding errors. 
For this reason, the second verification stage uses an overapproximation
with interval arithmetic with outward rounding. Thus, the first verification
stage underapproximates and is used to generate counterexamples, and the
second stage overapproximates and provides proof that no counterexample
exists.
